Clicks and Cliques

### 2018-12-24 papersoul.Rnw
edit race chunk

The bottom panel of Figure \ref{eco} presents the U.S. GDP growth rate in 2008, 2009, and 2010. A similar pattern is observed in both panels, suggesting the economic dimension is less related with attachment during the economic crisis.
\begin{figure}[hbpt]
<<econ, dependson=c('data'), echo=FALSE,message=FALSE,warning=FALSE, fig.height=4>>=

des.wt.year <- svydesign(ids =~ 1, strata =~ QSB, weights =~ PROJWT, data = filter(soul,!is.na(PROJWT)))
vars  <- svyby( ~ ECONOMY + CCE, ~ YEAR, des.wt.year, svyvar, keep.var = TRUE, na.rm = T)  
vars <- mutate(vars[, 1:5], rho = with(vars, V2/sqrt(V1*V4)), gdp = c(-0.4,-3.5,3.0))

rhos.m <- gather(vars, variable, value,rho,gdp) %>% 
  select(YEAR, variable, value) %>% 
  mutate(variable =  factor(variable, labels = c('Attachment-Economy correlation', 'GDP Rate')
))

ggplot(data = rhos.m, aes(x = YEAR, y = value)) + 
  labs(x = "", y = "", title = 'Evolution of Attachment-Economy correlation and GDP') +
  geom_line() + geom_point() +
  facet_grid(facets = variable~., scales = 'free') + 
  ggtitle('Evolution of Attachment-Economy correlation and GDP')

@@

<<race, echo=FALSE, dependson=c( 'data' ), message=FALSE, fig.height=4>>=
#relation between attached prop of white people and propo of.afro

# QD10 ask for hispanic or not hispanic, QD111 ask for race, we combine both in QD111

aux <- soul$QD111

levels(aux)[c(4,6:10,15:17,19,20) ] <- 'Other'
levels(aux)[c(1,2,5,7,8,10) ] <- 'Non Response'
levels(aux)[2] <- 'Hispanic'
aux[soul$QD10 == 'Yes'] <- 'Hispanic'
soul$race  <- factor(aux)

wt <- with(subset(soul, !is.na(PROJWT) & YEAR!=2010), PROJWT/2 )
des.pro <- svydesign(ids=~1, strata=~QSB, weights=~wt, data=subset(soul, !is.na(PROJWT) & YEAR!=2010))

tab <- svyby(~race+CCEGRP2+CCE,~QSB, des.pro, svymean,keep.var=FALSE, na.rm=T)
tab$diver <- apply(tab[,grep('race',colnames(tab))], 1, function(x) -sum(x[x!=0]*log(x[x!=0])))
b <- merge(census.data,tab[,c('QSB','diver','statistic.raceWhite') ], by='QSB')

rho.div <- with(tab, round(cor(diver, statistic.CCE),2))

ggplot(data = tab, aes(x = diver, y = logit(statistic.CCEGRP2Attached))) + geom_point(size = I(5)) + theme(axis.text.y = element_text( size = I(10)) ) + labs( y = 'Proportion of Attach (logit scale)', x = 'Race diversity index') + geom_smooth(se = FALSE, method = 'lm', size = I(1))

>>>>

The bottom panel of Figure \ref{eco} presents the U.S. GDP growth rate in 2008, 2009, and 2010. A similar pattern is observed in both panels, suggesting the economic dimension is less related with attachment during the economic crisis.
\begin{figure}[hbpt]
<<econ, dependson=c('data'), echo=FALSE,message=FALSE,warning=FALSE, fig.height=4>>=
svydesign(ids =~ 1, strata =~ QSB, weights =~ PROJWT, data = filter(soul,!is.na(PROJWT))) %>% 
  svyby( ~ ECONOMY + CCE, ~ YEAR, design = ., svyvar, keep.var = TRUE, na.rm = T)  %>% data.frame() %>% select(1:5) %>% 
  mutate(rho = V2/sqrt(V1*V4), gdp = c(-0.4,-3.5,3.0)) %>% 
  gather(variable, value,rho,gdp) %>% 
  select(YEAR, variable, value) %>% 
  mutate(variable =  factor(variable, labels = c('Attachment-Economy correlation', 'GDP Rate')
)) %>% ggplot(aes(x = YEAR, y = value)) + 
  geom_line() + geom_point() +
  labs(x = "", y = "", 
       title = 'Evolution of Attachment-Economy correlation and GDP') +
  facet_grid(facets = variable~., scales = 'free') + 
  ggtitle('Evolution of Attachment-Economy correlation and GDP')

# des.wt.year <- svydesign(ids =~ 1, strata =~ QSB, weights =~ PROJWT, data = filter(soul,!is.na(PROJWT)))
# vars  <- svyby( ~ ECONOMY + CCE, ~ YEAR, des.wt.year, svyvar, keep.var = TRUE, na.rm = T)  
# vars <- mutate(vars[, 1:5], rho = with(vars, V2/sqrt(V1*V4)), gdp = c(-0.4,-3.5,3.0))
# 
# rhos.m <- gather(vars, variable, value,rho,gdp) %>% 
#   select(YEAR, variable, value) %>% 
#   mutate(variable =  factor(variable, labels = c('Attachment-Economy correlation', 'GDP Rate')
# ))
# 
# ggplot(data = rhos.m, aes(x = YEAR, y = value)) + 
#   labs(x = "", y = "", title = 'Evolution of Attachment-Economy correlation and GDP') +
#   geom_line() + geom_point() +
#   facet_grid(facets = variable~., scales = 'free') + 
#   ggtitle('Evolution of Attachment-Economy correlation and GDP')

@@

<<race, echo=FALSE, dependson=c( 'data' ), message=FALSE, fig.height=4>>=

#relation between attached prop of white people and propo of.afro

# QD10 ask for hispanic or not hispanic, QD111 ask for race, we combine both in QD111
aux <- soul$QD111
levels(aux)[c(4,6:10,15:17,19,20) ] <- 'Other'
levels(aux)[c(1,2,5,7,8,10) ] <- 'Non Response'
levels(aux)[2] <- 'Hispanic'
aux[soul$QD10 == 'Yes'] <- 'Hispanic'
soul$race  <- factor(aux)

soul %>% select(race, CCEGRP2, CCE, QSB,PROJWT, YEAR) %>% 
  filter(!is.na(PROJWT), YEAR!=2010)  %>% 
  mutate(wt = PROJWT/2) %>% 
  svydesign(ids=~1, strata=~QSB, weights=~wt, data=.) %>% 
  svyby(~race+CCEGRP2+CCE,~QSB, design = ., svymean,keep.var=FALSE, na.rm=T) %>%
  gather(race, prop, contains('race')) %>% 
  group_by(QSB) %>% 
  summarise(
    statistic.CCEGRP2Attached = first(statistic.CCEGRP2Attached),
    diver  = -sum( prop[prop > 0]*log(prop[prop>0]) )
  ) %>% 
  ggplot(aes(x = diver, y = logit(statistic.CCEGRP2Attached))) +
  geom_point(size = I(5)) + 
  geom_smooth(se = FALSE, method = 'lm', size = I(1)) +
  theme(axis.text.y = element_text( size = I(10)) ) + 
  labs( y = 'Proportion of Attach (logit scale)', x = 'Race diversity index')

# b <- merge(census.data,tab[,c('QSB','diver','statistic.raceWhite') ], by='QSB') # why?
# rho.div <- with(tab, round(cor(diver, statistic.CCE),2)) # what is used for??

# wt <- with(subset(soul, !is.na(PROJWT) & YEAR!=2010), PROJWT/2 )
# des.pro <- svydesign(ids=~1, strata=~QSB, weights=~wt, data=subset(soul, !is.na(PROJWT) & YEAR!=2010))
# 
# tab <- svyby(~race+CCEGRP2+CCE,~QSB, des.pro, svymean,keep.var=FALSE, na.rm=T)
# tab$diver <- apply(tab[,grep('race',colnames(tab))], 1, function(x) -sum(x[x!=0]*log(x[x!=0])))
# b <- merge(census.data,tab[,c('QSB','diver','statistic.raceWhite') ], by='QSB')
# 
# rho.div <- with(tab, round(cor(diver, statistic.CCE),2))
# 
# ggplot(data = tab, aes(x = diver, y = logit(statistic.CCEGRP2Attached))) + geom_point(size = I(5)) + theme(axis.text.y = element_text( size = I(10)) ) + labs( y = 'Proportion of Attach (logit scale)', x = 'Race diversity index') + geom_smooth(se = FALSE, method = 'lm', size = I(1))
